Analysis

### 2019-11-29 analysis.Rmd
ad h bar graph perceived salaries

ggplot(table_pertot, aes(as.factor(year), median)) +
      geom_bar(aes(fill = factor(ocup, levels=c(1,2), labels=c("Obrero", "Gerente"))), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Salario (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ")

+ # quitar nombre leyenda, autoexplicativo +

      coord_flip()

>>>>

bar <- ggplot(table_pertot, aes(as.factor(year),median)) +
      geom_bar(aes(fill = factor(ocup, levels=c(1,2), labels=c("Obrero", "Gerente"))), position = "dodge", stat="identity", width=.5)  +
      geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), group="Ocup"), position=position_dodge(width=0.5), vjust=-0.5) +
      theme_bw(base_size = 18) +
      scale_y_continuous(labels = scales::comma) +
      ylab('Salario (mediana)') + xlab('Años') +
      scale_fill_brewer(palette="Paired") +
      theme(legend.position="top") +
      labs(fill = " ") # quitar nombre leyenda, autoexplicativo +

bar
# Horizontal

table_pertot$ocup2 <- factor(table_pertot$ocup, levels=c(2,1), labels=c("Gerente", "Obrero"))

 ggplot(data=table_pertot, aes(x=reorder(as.factor(year),-median), y=median, fill=ocup2)) +
     geom_bar(position = 'dodge', stat='identity') +
     geom_text(aes(label=format(median, big.mark = ",", scientific = FALSE), y=0), position=position_dodge(0.9), hjust=-0.25) +
     theme_bw(base_size = 12) +
     scale_y_continuous(labels = scales::comma) +
     ylab('Salario percibido (mediana)') + xlab('Años') +
     scale_fill_brewer(palette="Paired") +
     theme(legend.position="top") +
     labs(fill = " ") +
    coord_flip()
